---
title: "Milestone 3"
author: "Samuel Lowry"
date: "10/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(janitor)
library(tidyverse)
library(readxl)
```

I am planning on helping with the David Hogg project, but due to the radio silence on his part this is my plan b. 

I'm probably going to study global health in addition to datascience through the social sciences, so I thought I would pull in some World Bank and WHO data. My data can be found in the raw data file. One is the governmental health expenditures by country as a percent of GDP. The other is for education. I will probably add other expenditure data as well, but I thought it would be cool to track changes in spending per country and then contextualize those changes. 

Below is a simple bar graph showing a random sample of 8 countries' health expenditures which I included just as a visual. A lot more is to come, but I just wanted something more than this text and my initial data. 
```{r}
education <- read_xls("API_SE.XPD.TOTL.GD.ZS_DS2_en_excel_v2_248171.xls", skip = 2) %>% clean_names()
health <- read_xlsx("health.xlsx", skip = 2) %>% 
  clean_names()
health_sample <- health %>% 
  sample_n(8)
```

```{r}
health_sample %>% 
  ggplot(aes(x = country, y = x2015)) +
  geom_col(fill = "darkblue") +
  labs(title = "Government Health Expenditures as Percentage of GDP",
       subtitle = "Random Sample of 8 Countries",
       caption = "Data from 2015",
       x = "Country",
       y = "Gov. Health Expenditure as Percentage of GDP")
  
```